Chum Populations

### 2015-11-14 paper/main.tex
working

\begin{tabular}{lrrrrr}
\toprule
{} & {} & \multicolumn{2}{c}{Aligned sequences} & \multicolumn{2}{c}{Genotyping rate}\\
Collection &  n   &            mean &        std &              mean &       std \\
\midrule
Hamma Hamma            &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
Lilliwaup Creek        &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
Nisqually Kalama Creek &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
Sherwood River Fall    &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
Sherwood River Summer  &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
Skookum Creek          &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
Snohomish River        &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
Squakum Creek          &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
Stillaguamish River    &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
Hoodsport Hatchery*    &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
\bottomrule
\multicolumn{6}{l}{*paired-end sequencing.}
\end{tabular}

@@

\begin{table}[H]
%\caption{\label{tab:table-name}Genetic diversity}
\caption{Genetic diversity} 
\begin{tabular}{lrr}
\toprule
{} & Heterozygosity &     Ne \\
\midrule
Hamma Hamma            &           0.30 &    339 \\
Lilliwaup Creek        &           0.34 &  5,959 \\
Nisqually Kalama Creek &           0.32 &    161 \\
Sherwood River Fall    &           0.33 &    319 \\
Sherwood River Summer  &           0.31 &    145 \\
Skookum Creek          &           0.33 &  1,788 \\
Snohomish River        &           0.32 &  2,122 \\
Squakum Creek          &           0.31 & $\infty$* \\
Stillaguamish River    &           0.30 &  1,001 \\
Hoodsport Hatchery     &           0.30 & $\infty$* \\
\bottomrule
\multicolumn{3}{l}{*small sample size (\textless10)}
\end{tabular}

@@

@@

>>>>

\begin{tabular}{lrrrrr}
\toprule
{} & {} & \multicolumn{2}{c}{Aligned sequences} & \multicolumn{2}{c}{Genotyping rate}\\
Collection &  n   &            mean &        std &              mean &       std \\
\midrule
Hamma Hamma            &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
Lilliwaup Creek        &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
Nisqually Kalama Creek &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
Sherwood River Fall    &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
Sherwood River Summer  &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
Skookum Creek          &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
Snohomish River        &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
Squakum Creek          &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
Stillaguamish River    &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
\midrule
Hoodsport Hatchery*    &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
\bottomrule
\multicolumn{6}{l}{*paired-end sequencing.}
5\end{tabular}

@@

\begin{table}[H]
%\caption{\label{tab:table-name}Genetic diversity}
\caption{Genetic diversity} 
\begin{tabular}{lrr}
\toprule
{} & Heterozygosity &     Ne \\
\midrule
Hamma Hamma            &           0.30 &    339 \\
Lilliwaup Creek        &           0.34 &  5,959 \\
Nisqually Kalama Creek &           0.32 &    161 \\
Sherwood River Fall    &           0.33 &    319 \\
Sherwood River Summer  &           0.31 &    145 \\
Skookum Creek          &           0.33 &  1,788 \\
Snohomish River        &           0.32 &  2,122 \\
Squakum Creek          &           0.31 & $\infty$* \\
Stillaguamish River    &           0.30 &  1,001 \\
\midrule
Hoodsport Hatchery     &           0.30 & $\infty$* \\
\bottomrule
\multicolumn{3}{l}{*small sample size (\textless10)}
\end{tabular}

@@

\begin{figure}[H]
%\includegraphics[scale=.35]{figures/supplemental/recombination_landscape.fam_08.png}
\caption[SUPPLEMENTAL - Centromere placemet - y plots]{ Centromere placemet - y plots}
\end{figure}

@@

\begin{figure}[H]
\caption[SUPPLEMENTAL - Genome scan - Bayescan Fst]{ Centromere placemet - y plots}
\end{figure}

\begin{figure}[H]
\caption[SUPPLEMENTAL - Q plot - ancestry coefficients]{Ancestry coefficients}
\end{figure}

\begin{table}[H]
\caption[SUPPLEMENTAL - centromere placement]{Centromere placement}
\end {table}

\begin{table}[H]
\caption[SUPPLEMENTAL - Procrustes analysis]{Procrustes analysis}
\end {table}
